Project assignment - Tahoe-LAFS with SHA-3 candidates

### 2010-12-15 paper/main.tex
Proper order of tables reffing

The numbers for uploading and downloading the different file vectors are
summarized in Tables \ref{tbl:hashingtimes:put1gb},
\ref{tbl:hashingtimes:get1gb}, \ref{tbl:hashingtimes:put100mb},
\ref{tbl:hashingtimes:get100mb}, \ref{tbl:hashingtimes:put1mb},
\ref{tbl:hashingtimes:get1mb}, \ref{tbl:hashingtimes:put1kb},
\ref{tbl:hashingtimes:get1kb}, \ref{tbl:hashingtimes:put1b} and
\ref{tbl:hashingtimes:get1b}.  The third column contains the time spent doing
other operations than hashing, i.e. \emph{Time spent not hashing = Total time -
Time spent hashing}. \emph{Fraction} displays the part of total time the calls
to the hashing libraries take.

>>>>

The numbers for uploading and downloading the different file vectors are
summarized in Tables \ref{tbl:hashingtimes:put1b}, \ref{tbl:hashingtimes:get1b},
\ref{tbl:hashingtimes:put1kb}, \ref{tbl:hashingtimes:get1kb},
\ref{tbl:hashingtimes:put1mb}, \ref{tbl:hashingtimes:get1mb},
\ref{tbl:hashingtimes:put100mb}, \ref{tbl:hashingtimes:get100mb},
\ref{tbl:hashingtimes:put1gb} and \ref{tbl:hashingtimes:get1gb}. The third
column contains the time spent doing other operations than hashing, i.e.
\emph{Time spent not hashing = Total time - Time spent hashing}. \emph{Fraction}
displays the part of total time the calls to the hashing libraries take.
